---
title: "Getting started"
author: "Nathan Day"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  comment = "#",
  options(repos="https://cran.rstudio.com" )
)
```

# sesh

Is a light-weight tool for tracking R packages. It sits somewhere between `reprex` and `packrat` and revolves around `CSV` files to store key package information.

The main goal of `sesh`, is to make it simpler to reproduce R code. The ability to restore specific versions/commits of packages, with minimal overhead, is security for rapid development.

```{r load_sesh, eval = F}
devtools::install_github("nathancday/sesh")
```

```{r, eval = F}
library(sesh)
```

```{r, echo = F}
devtools::load_all("~/future/sesh/")
```


### Purpose

The concept behind `sesh` is being able to record information about specific package versions for sharing with others, including your future self.

Using `sesh` as part of your workflow gives you extra a little extra reprodu-security at the individual Rscript level.

It is very similar in aim to `packrat`, but doesn't tie you into a RStudio Project. Instead of re-installing all of the required packages for each project, `sesh` checks against currently installed versions and builds a disposable library path for itself in `~/.Trash/` if matching versions are required.

It does not touch R's deafult package search path.

### Demo

We start by loading `forcats` and `tibble` from their current CRAN versions, just so we have some packages beyond R-core.

```{r load_examples, message = F}
library(forcats) # v0.3.0
library(tidyr) # v0.8.1
```

##### Saving critial packages for your script

`session_info()` is an improvement on `sessionInfo()` for readability, but is still fairly verbose.

`sesh` aims to filter this output to only the attached packages. It also captures information about the current `R-core` version.

```{r sesh}
sesh()
```

This dataframe is the essense of `sesh`, a light, easy to share, record of your R session's essential information.

##### Saving your `sesh`

To save your current `sesh()`, use `save_sesh()`.

It will record the vital information to re-load all of your attached `pacakge@verion`s and write it to disk as a `CSV`.

```{r save_easy, message = T}
save_sesh()
```

The default `path`, is set up to name the output as "sesh_$SYS-DATE.csv". But it uses the [`glue`](https://github.com/tidyverse/glue) package to paste together R variables, so you could include custom gloabls to fit your tastes.

##### Checking out an old `sesh`

Just to show off the tools, let's re-check the `CSV` we just saved for our current `sesh`.

The function `check_sesh()` will compare the currently loaded/installed package versions against a `sesh` record. It will report which packages are already loaded, installed or require installation.

```{r check_easy, message = T}
check_sesh("sesh_2018-08-19.csv") # check against currently installed versions
```

This just confirms our current session info matches the session info we saved two seconds ago, duh.

##### Simulated time travel

Let's pretend we are visiting a past script and let's pretend we wrote that past script sometime after `forcats` intial realse, Aug 29, 2016.

To re-create this scenario, we will re-install two common cases:

* a prior CRAN release version
* a package from GitHub at prior commit

```{r mess_up, eval = F}
devtools::install_version("forcats", "0.1.0", reload = F)
devtools::install_github("tidyverse/tidyr@bd0c6b09052e91a4d283b2be6c8d3c5a6769b910", reload = F)
```

It is a good idea to restart your R session whenever you install an already attached package, like now.

```{r re-load, eval = F}
library(forcats)
library(tidyr)

save_sesh("sesh_2017-10-01.csv")
```

##### Ending time warp

Bringing us back to back to now.

```{r back_to_now, eval=F}
install.packages("forcats")
install.packages("tidyr")

library(forcats)
library(tidyr)
```

##### Pretend pick up

So now let's pretend we are picking up that year-old, dusty script.

```{r}
read_sesh("sesh_2017-10-01.csv")
```
 
 Sure, we are a little nervous because perhaps by upgrading our package versions we have inadvertantly broken something.

But our new found `sesh`abilities make dealing with diffs simple and straight forward.

##### Check list

In order to see what pacakges are differnt between the "old script" and our library today, use `check_sesh`.

```{r re-check, message = T}
check_sesh("sesh_2017-10-01.csv")
```

That's shows us the difference between our currently installed versions and the "past" versions.

The function `install_sesh()` will re-install matching versions. By looking at `source` and `version`, it will attempts to install the sesh version in `~/.Trash/` and tell you if it was succesful. By keeping a temporary library in  `~/.Trash/`, `sesh` contains conflicts and doesn't take up disk space long term, because `macOS` deletes any files in there after 30 days.

`sesh` does not touch `.libPaths()`, so it will not interfer with your globally installed package versions.

```{r install, cache = F}
install_sesh("sesh_2017-10-01.csv")
```

Great, now we have the the right package versions installed to rerun our "old" script, but as it sits right now the matching versions are not loaded.

We need to call `sesh_load()` to attach them. We should also restart the R session again because we re-installed loaded packages.

```{r echo = F}
unloadNamespace("forcats")
unloadNamespace("tidyr")
```

```{r, message=T}
load_sesh("sesh_2017-10-01.csv")
```

And re-checking we see...

```{r, message=T}
check_sesh("sesh_2017-10-01.csv")
```

All that is left to do now is source that old script!

##### Un-seshing

When you are done working with the past `sesh` versions, you can go back to your current global versions immediately. Just restart your R session and attach your libraries like normal.

There is also the helper function `unload_sesh()` to do this without restarting, but it's vunerable to `dependencies`,

```{r}
unload_sesh("sesh_2017-10-01.csv")

library(forcats)
library(tidyr)

sesh()
```

